---
title: "README"
author: "Sara Colom"
date: "`r Sys.Date()`"
output: 
  github_document:
    df_print: kable
---

This repo contains the source function to generate one or two-way cross tab summary stats on the fly with `var_summarise()`

# Installation

Make sure you have `devtools`, `credentials` and `remotes` already installed and loaded. Also be sure to be active on the **UCSF VPN**.

  - `install.packages("devtools")`
  - `install.packages("credentials")`
  - `install.packages("remotes"`
  - `library(devtools)`
  - `library(credentials)`
  - `library(remotes)`

Steps are commented out below beneath its description.

```{r}
#set config
# usethis::use_git_config(user.name = "YourName", user.email = "your@mail.com")

#Go to github page to generate token
# usethis::create_github_token() 

#paste your PAT into pop-up that follows...
# credentials::set_github_pat()

#now remotes::install_github() will work
# remotes::install_github("ucsf-bhhi/SummaryTable")
```


# Examples


This package was created to generate summary statics tables for one to two-cross tabs on the fly. You need to provide a data set with the variables you want to summarise.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Read in library

```{r}
library(SummaryTable)
library(dplyr)
```


## Example

### Data: iris

This is the output for `Sepal.Width` a continuous variable w/o stratification. Without any other sepcification, the function spits out the mean and SD.

```{r}
var_summarise(dat = iris, var = "Sepal.Width")
```

